### 2023-10-11 README.Rmd
add docker CI

@@

## Reputational Risk and Questionable Research Practices in Archaeological Science.

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

[![Docker build status](https://github.com/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/workflows/.github/workflows/render-in-docker.yml/badge.svg)](https://github.com/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/actions)

@@

### Reputational Risk and Questionable Research Practices in Archaeological Science.

@@

> Marwick, B., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_ Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
